---
title: "Pilgrim Predictive Analytics"
author: "Uros Randelovic, Daniel R Mangoubi, Annabelle Zhang, Roopa Boodhun"
date: "November 13, 2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Pilgrim Bank pilgrimData: For the current assignment, read Pilgrim Bank Case A and Pilgrim Bank
Case B from the Harvard CoursePack. We would be using the pilgrimData in the file "Pilgrim Bank (A),
(B) & (C) - Spreadsheet Supplement". Your report should at least cover the following details -

###1. What is Pilgrim Bank's pilgrimData problem? What is the final managerial objective?
##### The Pilgrim Bnak's pilgrimData probelm is that some of the variables include NA values due to the customers who dropped out from 1999 to 2000. This problem is going to make the later pilgrimData analysis and interpretations more difficiult. Thus, we might need to drop the NA values and perform a separate analysis on the NA values in addition to the completed pilgrimDatas. There are also missing values for age and income which is another problem with the pilgrimData. The final managerial objective is to determine whether the use of the electronic billpay product have any incremental impact on performance. 

###2. Describe the measurement types of each variable
```{r}
str(pilgrimData)
```
##### ID: Nominal Variable
##### 9Profit and 0Profit: Ratio
##### 9Age: Ordinal
##### 9Inc: Ordinal
##### 9Tenure: Ratio
##### 0Online: Nominal (Binary)
##### 9Billpay and 0Billpay: Nominal (Binary)


###3. How do you handle missing pilgrimData in this pilgrimDataset? Clearly mention if you are using pilgrimData
##### Our group drops the pilgrimData with NA for any 2000 variables such as 0Billpay, because those are the people who stop being customers of the bank. However, our group still need these pilgrimData for performing further analysis on retention. 
##### Additionally, our group fills in the NA 9Age with the median 9Age, and NA 9Inc with the median 9Inc. Thus, these values have no effect on the summary statistics of the dataset. 
##### Overall, our group drops any data which has NA in 0Online, 0Profit, and 0Billpay. We fill in the NA in 9Age and 9Inc with according median values. This strategy allows us to have a large enough dataset to work with rather than drop every data with any kind of NA. 
```{r}
pilgrimData <- read.csv("C:/Users/Uros Randelovic/Documents/R workspace/BUS 111/pilgrim2/Data.csv",
                       stringsAsFactors=F, na.strings=c(NA,"NA"," NA"))

#filling in the NAs with NULL
pilgrimData[is.na(pilgrimData)]= "NULL"

#fillinf in the median of X9Age for NULL X9Age, then generate the X9Age colunm into x9Age column
medianAge = median(pilgrimData$X9Age[pilgrimData$X9Age!="NULL"])
pilgrimData$x9Age = pilgrimData$X9Age
pilgrimData$x9Age[pilgrimData$X9Age=="NULL"]<- medianAge

#repeat the same with income , then generate the X9Inc into x9Inc column
medianInc = median(pilgrimData$X9Inc[pilgrimData$X9Inc!="NULL"])
pilgrimData$x9Inc = pilgrimData$X9Inc
pilgrimData$x9Inc[pilgrimData$X9Inc=="NULL"]<- medianInc
retainedCustomers=pilgrimData[pilgrimData$X0Billpay !="NULL",]

pilgrimData$x9Age <- as.numeric(pilgrimData$x9Age)
pilgrimData$x9Inc <- as.numeric(pilgrimData$x9Inc)

#add a dummy if the cusotmer left (1) stayed (0)
pilgrimData$left <- 0
pilgrimData$left[pilgrimData$X0Billpay=="NULL"] <- 1
#generate retained column, which is the opposite of left column
pilgrimData$retained <- 0
pilgrimData$retained[pilgrimData$left==0] <- 1

```

###4. Provide a brief summary of takeaways from Interim Deliverable-I. These could include key summary statistics tables or plots.
```{r}
#online banking customers
table(pilgrimData$X9Online)
table(pilgrimData$X0Online)
#profit
pilgrimData$X0Profit <- as.numeric(pilgrimData$X0Profit)
summary(pilgrimData$X9Profit)
summary(pilgrimData$X0Profit)
#billpay
pilgrimData$X0Billpay <- as.numeric(pilgrimData$X0Billpay)
table(pilgrimData$X9Billpay)
table(pilgrimData$X0Billpay)
```
##### Online banking: In 1999, there are 3854 online banking customers, and 27780 offline banking customer. The online banking customers is 12.18% (3854/(3854+27780)) of all customers. In 2000, there are 5256 online banking customers, and 21159 offline banking customers. The online banking customers is 19.90% (5256/(5256+21159)) of all customers. Thus, based on the basic summary statics our group present, there this an increase in the percentage of online banking customers vs. all customers. 
##### Profit: The mean and the median profit of 1999 are 111.5 and 9.0. The mean and the median profit of 2000 are 144.8 and 23.0. Both the meadian anf the mean profit have increased over the year. In addition, since there is no NULL for X9Profit, there are no customers who are not 1999 customers but are added for 2000. 
##### Billpay: In 1999, there are 528 electronic billpay customers, and 31106 paper billpay banking customer. The electronic billpay customers is 1.67% (528/(528+31106)) of all customers. In 2000, there are 798 electronic billpay  customers, and 25617 paper billpay customers. The electronic billpay  customers is 3.02% (798/(798+25617)) of all customers. Thus, based on the basic summary statics our group present, there this an increase in the percentage of electronic billpay customers vs. all customers. 

```{r}
#corrplot

library(corrplot)

corrdata <- read.csv("C:/Users/Uros Randelovic/Documents/R workspace/BUS 111/pilgrim2/data.csv",
                       stringsAsFactors=F, na.strings=c(NA,"NA"," NA"))

#we dropped all the NA values to performe the correlation analysis 
corrdata <- corrdata[complete.cases(corrdata[c("X9Profit","X0Profit","X0Online","X0Billpay","X9Inc",
                                               "X9Online","X9Age","X9Tenure")]),]

#this is to check if there were any factors that correlate with the people staying or not
View(corrdata)
df <- subset(pilgrimData,select = c(X9Profit,X9Online,x9Age,x9Inc,left, X9Billpay))
df$x9Age <- as.numeric(df$x9Age)
df$x9Inc <- as.numeric(df$x9Inc)
View(df)
corrplot(cor(df), method="number",shade.col=NA, tl.col="black", tl.srt=45)
```
##### Besed on the presented correlation table, our group concludes that there is no strong correlation among variables. The strongest correlation based on the table is the positive correlation between X9Online and X9Billpay of 0.35.
#################################################################Annabelle above#####################################################################
#####################################################################################################################################################

5. Compare the mean profitability of customers for the years 1999 and 2000 by their
enrollment status in online banking or electronic billpay for those years. Clearly mention 
the type of two-sample t-test you would be using, the null and alternate hypotheses for
these tests. Interpret the results of these t-tests.
```{r}
#two-sample t-test you would be using - explanation of the three tests again

#two independet sample t test


#two paird sample t test


```
6. Determine whether the use of the online channel affected customer profitability and
retention in 1999. Clearly state the dependent and independent variables used in your
regression analysis. Interpret the findings of this analysis, and note the R-squared.
```{r}
#the issue here is that the online is not relevant to any - go to the graph



#model 1 - predicting the profit based on if the people were online or not 
model1 = lm(pilgrimData$X9Profit ~ pilgrimData$X9Online)
summary(model1)

```



```{r}
#ask if this is correct 
library(caTools)

model2 <- glm (pilgrimData$left ~ pilgrimData$X9Online, family = binomial)
summary(model2)

```
In the table above the coefficient on X9Online is -0.20315.  





7. You may extend this analysis by further controlling for omitted variable biases. Mention
which variables you are using as controls, and re-do the regression from part (6) after
adding these controls. Interpret your findings and note the change in R-squared. [Hint:
For this part, you may split your pilgrimData into "train" and "test" pilgrimDatasets, and comment on
which regression model provides the best fit. Alternatively, you may use any of likelihood
or Information Criterion techniques discussed in class.]
```{r}
#how do we control for the pilgrimData

#splitting the data to build a model
smp_size <- floor(0.75 * nrow(pilgrimData))
## set the seed to make your partition reproductible
set.seed(123)
train_ind <- sample(seq_len(nrow(pilgrimData)), size = smp_size)
#separate specific sets of data
train <- pilgrimData[train_ind, ]
test <- pilgrimData[-train_ind, ]





testModel1 = lm(pilgrimData$X0Profit ~  pilgrimData$X9Profit, pilgrimData$x9Age, pilgrimData$x9Inc, pilgrimData$X9Tenure)




```
8. What is the predicted customer profitability and likelihood of retention, given your
regression model? How does it compare with actual customer profitability and retention
in 2000?
```{r}
#have  the profits for retained not the if they stayed or not 



```
9. Summarize your findings for Pilgrim Bank's managers, and make recommendations for
their customer Internet strategy